Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-25 paper/paper.tex
#28 minimum baseline results

We can see in Column (1) that switching states has no immediate effect on the probability of recorded construction activity. Over the next two centuries, however, the effect grows positive and significant: 100 years after a city switches states, the probability of construction activity is 5 percentage points higher than in cities that did not switch. After 200 years this difference grows to 9 percentage points. These estimates are significant at the 5 percent and 1 percent level, respectively. Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise these dynamics. It looks similar to Figure BLANK, taken from \cite{schoenholzer2022}, except for the missing short-run drop. Note, however, that the outcome variable in their regression is population, which could be more sensitive to short-run effects --- after all, people may die or leave the city at an increased rate in times of political turmoil and conflict.

@@

Table \ref{tab:baseline_50y} shows estimates from Equation \eqref{eq:baseline}. This is a difference-in-differences specification with interactions to capture heterogeneous treatment effects. As before, different columns use different subsets of construction as the outcome variable.

I report estimates of the coefficient of interest $\theta_{conquest}$ in the second row.

>>>>

We can see in Column (1) that switching states has no immediate effect on the probability of recorded construction activity. Over the next two centuries, however, the effect grows positive and significant: 100 years after a city switches states, the probability of construction activity is 5 percentage points higher than in cities that did not switch. After 200 years this difference grows to 9 percentage points. These estimates are statistically significant at the 5\% and 1\% level, respectively. Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise these dynamics.

@@

Table \ref{tab:baseline_50y} shows estimates from Equation \eqref{eq:baseline}. This is a difference-in-differences specification with added interactions to capture heterogeneous treatment effects. As before, different columns use different subsets of construction as the outcome variable.

I report estimates of the coefficient of interest $\theta_{conquest}$ in the second row. In Column (1) we can see that the probability of construction activity in a given period is 4 percentage points higher following a conquest vis-a-vis after a succession, but the difference is not statistically significant.

The only subset of construction that shows a significant effect is state construction --- palaces, castles, military and administrative buildings. We can see in Column (2) that these are 5 percentage points \textit{less} likely to be built in a city after it was conquered; the effect is significant at the 5\% level.
